%
%Academic CV LaTeX Template
% Author: Dubasi Pavan Kumar
% LinkedIn: https://www.linkedin.com/in/im-pavankumar/
% License: MIT
%
% For errors, suggestions, or improvements, please contact:
% Email: pavankumard.pg19.ma@nitp.ac.in
%



\documentclass[a4paper,12pt]{article}

% Package imports
\usepackage{latexsym}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
    % \setlist[itemize]{itemsep=1pt, parsep=0pt}
    % \setlist[enumerate]{itemsep=1pt, parsep=0pt}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}

%%%%%%% Fonts %%%%%%%%%%%%
% For symbols
\usepackage{fontawesome5}
% Math stuff
\usepackage[sc]{mathpazo}
\usepackage{amsmath, amssymb, amsfonts}
% Optional: Microtype for better typography
\usepackage{microtype}

% PDFLATEX
    \usepackage[T1]{fontenc}


% % Font and Language support for XeLaTeX
%     \usepackage{fontspec} % Font support for XeLaTeX
%     \setmainfont{Noto Serif} % Set a specific font (system font)
%     % Language support
%     \usepackage{polyglossia}
%     \setmainlanguage{english}

\usepackage{xcolor}
% Color definitions
\definecolor{darkblue}{RGB}{0,0,139}

% Page layout
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=2cm, right=1.2cm, bottom=2cm}
\setlength{\footskip}{5pt} % Addressing fancyhdr warning

% % Hyperlink setup (moved after fancyhdr to address warning)
% \usepackage[hidelinks]{hyperref}
% \hypersetup{
%     colorlinks=true,
%     linkcolor=darkblue,
%     filecolor=darkblue,
%     urlcolor=darkblue,
% }

% Custom box settings
\usepackage[most]{tcolorbox}
\tcbset{
    frame code={},
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!20,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=-2mm,
    boxsep=4pt,
    arc=0pt,outer arc=0pt,
}
% Set the citation style
\usepackage[
    backend=biber,      % Specifies the backend to be used by BibLaTeX for processing the bibliography. 'biber' is the default backend.
    maxnames=20,        % Limits the maximum number of author names to display before abbreviating with "et al."
    style=nature,       % Sets the citation style to 'nature,' which is commonly used in scientific papers.
    sorting=ydnt,       % Specifies the sorting order of entries in the bibliography:
                        % y - year (descending)
                        % d - descending order
                        % n - name
                        % t - title
    defernumbers=true,  % Delays the assignment of citation numbers until the end of the document, allowing for the correct order of citations within each bibliography section.
]{biblatex}
\addbibresource{ref.bib} % Adds the bibliography resource file 'ref.bib' containing all the references.
\renewcommand{\bibfont}
{\normalfont\small}
% URL style
\urlstyle{same}

% Text alignment
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\circ$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*,labelsep=1mm,itemsep=0.5mm]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

% Commands for icon sizing and positioning
\newcommand{\socialicon}[1]{\raisebox{-0.05em}{\resizebox{!}{0.8em}{#1}}}
\newcommand{\ieeeicon}[1]{\raisebox{-0.3em}{\resizebox{!}{1.3em}{#1}}}

% Font options
\newcommand{\headerfonti}{\fontfamily{phv}\selectfont} % Helvetica-like (similar to Arial/Calibri)
\newcommand{\headerfontii}{\fontfamily{ptm}\selectfont} % Times-like (similar to Times New Roman)
\newcommand{\headerfontiii}{\fontfamily{ppl}\selectfont} % Palatino (elegant serif)
\newcommand{\headerfontiv}{\fontfamily{pbk}\selectfont} % Bookman (readable serif)
\newcommand{\headerfontv}{\fontfamily{pag}\selectfont} % Avant Garde-like (similar to Trebuchet MS)
\newcommand{\headerfontvi}{\fontfamily{cmss}\selectfont} % Computer Modern Sans Serif
\newcommand{\headerfontvii}{\fontfamily{qhv}\selectfont} % Quasi-Helvetica (another Arial/Calibri alternative)
\newcommand{\headerfontviii}{\fontfamily{qpl}\selectfont} % Quasi-Palatino (another elegant serif option)
\newcommand{\headerfontix}{\fontfamily{qtm}\selectfont} % Quasi-Times (another Times New Roman alternative)
\newcommand{\headerfontx}{\fontfamily{bch}\selectfont} % Charter (clean serif font)

% Hyperlink setup (moved after fancyhdr to address warning)
\usepackage[hidelinks]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=darkblue,
    filecolor=darkblue,
    urlcolor=darkblue,
    citecolor=darkblue
}





\begin{document}

% Uncomment if using PDFLATEX
    \headerfontiii

% Header
\begin{center}
    {\Huge\textbf{MEGHAVARSHINI KRISHNASWAMY}}
\end{center}
\vspace{3mm}

% \noindent
\begin{minipage}[t]{0.4\textwidth}
    % \small{
        EDSI, University of Maryland, College Park\\
        Center for Educational Data Science and Innovation\\ 
        Suite 0102, Benjamin Building\\ 
        College Park, Maryland - 20740, USA
    % }
\end{minipage}%
\hfill
\begin{minipage}[t]{0.35\textwidth}
    \small{
        \socialicon{\faEnvelope} \href{mailto:mkswamy@umd.edu}{mkswamy[at]umd.edu}\\
        \socialicon{\faGraduationCap} \href{https://edsi.umd.edu/directory/megh-krishnaswamy}{megh-krishnaswamy}\\
        \socialicon{\faLinkedin} \href{www.linkedin.com/in/meghavarshini-krishnaswamy}{meghavarshini-krishnaswamy}\\
        \socialicon{\faGithub} \href{https://github.com/meghavarshini}{meghavarshini}\\
        \socialicon{\faGlobe} \href{https://meghavarshini.github.io}{meghavarshini.github.io}    
        }
\end{minipage}

\section{\textbf{Objective}}\label{objective}
\vspace{1mm}
\small{
I am a computational linguist and phonetician. I am interested in an interdisciplinary research career and mentorship role, where I can work with language and behavioural data, and applied computational methods. I want to mentor the next generation of scientists, with a focus on data science principles, project management, and quantitative and qualitative methods for human subject data collection. I aim to add to their knowledge and experience in experimental and applied linguistics.
}
\vspace{-2mm}

\section{\textbf{Education}}\label{education}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeSubheading
{University of Arizona}{Tucson Arizona, USA}
{PhD, Linguistics}{Aug 2019--July 2025}
\resumeItemListStart
\item GPA: 3.9/4.00
\resumeItemListEnd

\resumeSubheading
{University of Arizona}{Tucson Arizona, USA}
{MS, Human Language Technology}{Aug 2019--May 2021}
\resumeItemListStart
\item GPA: 3.9/4.00
\resumeItemListEnd

\resumeSubheading
{The English and Foreign Languages University}{Hyderabad, India}
{MA, Linguistics}{July 2013--May 2015}
\resumeItemListStart
\item GPA: 72.9\%
\resumeItemListEnd

\resumeSubheading
{University of Delhi}{New Delhi, India}
{BA (Hons.), English}{July 2010--June 2013}
\resumeItemListStart
\item Score: 59.8\%, II-Division
\resumeItemListEnd
\resumeSubHeadingListEnd
\vspace{-8mm}

\section{\textbf{Professional Affiliations and Experience}}\label{professional-affiliation-experience}
\vspace{-0.4mm}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Center for Educational Data Science and Innovation,  [\href{https://edsi.umd.edu}{\faIcon{globe}}]}{College Park}
        {Postdoctoral Associate}{Aug 2025 - }
        \resumeItemListStart
          \item Provide language science expertise for providing teachers data-driven teaching feedback.
          \item Building pipelines for building speech models for automatic speech recognition of children's speech. 
          \item Set up linguistic and phonetic analysis on spoken and written communications generated in K12 teaching environments.
    \resumeItemListEnd

    \resumeSubheading
        {SPLANG Phonetics Lab (phonetics and psycholinguistics), EFL University\textbf{}}{Hyderabad, India}
        {Research Associate}{Oct 2017 - Aug 2019}
        \resumeItemListStart
          \item Designed and conducted acoustic phonetics experiments for languages such as Bengali, Mongolian, Malayalam and Hindi.
          \item Conducted corpus analysis and qualitative assessments on multi-lingual internet corpora to find stimuli for experiments.
          \item Created audio stimuli using Praat and ffmpeg for eye-tracking experiments and perception tasks.
          \item Wrote R and Python scripts for statistical analysis and data visualisation.
          \item Co-authored papers, conference posters, research proposals and presentations.
          \item Provided training to students for experimental modalities such as ultrasound, eye-tracking, and speech perception and production.
          \item Managed administrative tasks such as purchase requests, lab equipment setup, documentation for datasets, scheduling lab activities, and drafting the lab's budget and spending.  
          \item My research contributed to publication \cite{dutta2019articulatory, gp2023mismatch, mitracoarticulation, krishnaswamy2018active, krishnaswamy2020alveolar}.
    \resumeItemListEnd
  
\resumeSubHeadingListEnd
\vspace{-8mm}

\section{\textbf{Academic Research Experience}}\label{academic-research-experience}
\vspace{-0.4mm}
  \resumeSubHeadingListStart

    \resumeSubheading
        {Center for Educational Data Science and Innovation,  [\href{https://edsi.umd.edu}{\faIcon{globe}}]}{College Park}
        {Postdoctoral Associate}{Aug 2025 - }
        \resumeItemListStart
          \item Provide language science expertise for providing teachers data-driven teaching feedback.
          \item Building pipelines for building speech models for automatic speech recognition of children's speech. 
          \item Set up linguistic and phonetic analysis on spoken and written communications generated in K12 teaching environments.
    \resumeItemListEnd

    \resumeSubheading
          {{Data Science Institute [\href{https://datascience.arizona.edu}{\faIcon{globe}}]}}{Tucson, USA}
          {Graduate Research Assistant (educator and consultancy)}{Aug 2023--July 2025}
          \resumeItemListStart
            \item Designed and delivered technical workshops encompassing NLP, python programming, command line interface proficiency, version control, High Performance Computing (HPC), and AI tools for research. See associated Github repository \href{https://github.com/ua-datalab/NLP-Speech}[\href{https://github.com/ua-datalab/NLP-Speech}{\faGithub}].
            \item Collaborated in creating a language processing pipeline for quantum NLP applications in low-resource languages.
            \item Spearheaded a collaboration with computational linguistics faculty, for improving HPC understanding and knowledge.
            \item Provided consulting services for university research projects (data science and NLP), for the successful execution and optimization of these projects.
    \resumeItemListEnd 
 
    \resumeSubheading
        {DARPA ASIST-ToMCAT Project (NLP) [\href{https://ml4ai.github.io/tomcat}{\faIcon{globe}}]}{Tucson}
        {Graduate Research Assistant}{May 2020 - Dec 2023}
        \resumeItemListStart
          \item Conducted doctoral research on the efficacy of using neural network models for speech synchrony/vocal entrainment in spontaneous conversations \cite{krishnaswamy2025}.
          \item Contributed code, research insights, and qualitative assessments for vocal feature extraction using OpenSMILE, Praat and Python.
          \item Reported on the viability of different voice recording platforms for collecting human subject data and automatic transcriptions, and performed quality assessments.
          \item Performed literature reviews and assessed datasets for multimodal sentiment and emotion classification projects.
          \item Provided documentation and writing for effective communication of our research findings for DARPA Principal Investigators (PIs) Meetings and Github documentation.
          \item Contributed research to publications presented at NeurIPS, NAACL, and ICML: \cite{multicat, pyarelal2023tomcat,soares2024probabilistic,culnan2021me, krishnaswamy2025lstm}.
    \resumeItemListEnd

    \resumeSubheading
        {Douglass Phonetics Lab (applied linguistics)) [\href{https://ml4ai.github.io/tomcat}{\faIcon{globe}}]}{Tucson}
        {Graduate Research Assistant}{Jan 2020 - Dec 2020}
        \resumeItemListStart
          \item Coordinated the lab's ongoing phonetics experiments and data collection.
          \item Initiated the migration of the lab's experiments to remote platforms (like Finding Five) during the pandemic, and assessed their viability.
          \item Provided training and technical support to undergraduate researchers.
          \item Contributed documentation for the data exploration and statistical analysis.
          \item Conducted transcription and extraction of phonetic data on Praat.
          \item My research contributed to publication \cite{krishnaswamy2023perception}.
\resumeItemListEnd

    \resumeSubheading
        {SPLANG Phonetics Lab (phonetics and psycholinguistics), EFL University\textbf{}}{Hyderabad, India}
        {Research Associate}{Oct 2017 - Aug 2019}
        \resumeItemListStart
          \item Designed and conducted acoustic phonetics experiments for languages such as Bengali, Mongolian, Malayalam and Hindi.
          \item Conducted corpus analysis and qualitative assessments on multi-lingual internet corpora to find stimuli for experiments.
          \item Created audio stimuli using Praat and ffmpeg for eye-tracking experiments and perception tasks.
          \item Wrote R and Python scripts for statistical analysis and data visualisation.
          \item Co-authored papers, conference posters, research proposals and presentations.
          \item Provided training to students for experimental modalities such as ultrasound, eye-tracking, and speech perception and production.
          \item Managed administrative tasks such as purchase requests, lab equipment setup, documentation for datasets, scheduling lab activities, and drafting the lab's budget and spending.  
          \item My research contributed to publication \cite{dutta2019articulatory, gp2023mismatch, mitracoarticulation, krishnaswamy2018active, krishnaswamy2020alveolar}.
    \resumeItemListEnd
  
\resumeSubHeadingListEnd
\vspace{-8mm}

\section{\textbf{Teaching Experience}}\label{teaching-experience}
\vspace{-0.4mm}
\resumeSubHeadingListStart

\resumeProject
      {LING314: Phonetics, [Instructor on record] }
      {Tools: D2L, Praat, Qualtrics}
      {Jan 2023 - May 2023}
      {{}[\href{https://linguistics.arizona.edu/course/ling-314-phonetics}{\textcolor{darkblue}{\faGlobe}}]}
    \resumeItemListStart
       \item Introduced core topics in phonetic science and the articulation, acoustic processing, and perception of human speech, with a focus on the prosodic properties and the phonetic structure of different dialects of English.
       \item Taught the fundamentals of transcribing sound patterns with the International Phonetic Alphabet and the terminology for phonetic features.
       \item Lead lab sessions to collect, process, and analyze acoustic features, and read spectrograms for different consonants and vowels.
    \resumeItemListEnd

\resumeProject
      {LING432 (5-week, online), Psychology of Language [Instructor on record]}
      {Tools: D2L, Panopto, Zoom whiteboard and quizzes }
      {Summer 2022 and 2023}
      {{}[\href{https://philosophy.arizona.edu/course/phil-432-psychology-language}{\textcolor{darkblue}{\faGlobe}}]}
    \resumeItemListStart
       \item Introduced topics in language processing.
       \item Created teaching materials on comprehension and production of sounds, words, and sentences, and the psychological processes involved.
       \item Lead discussions on bilingual processing, speech errors, and artificial speech.
       \item Designed student assignments and quizzes, and provided feedback on academic writing.
       \item Recorded weekly lectures on Panopto.
    \resumeItemListEnd
  
  \resumeProject
      {LING150, Language and the World [Grader]}
      {Tools: D2L, Panopto, MS Office suite }
      {Aug - Dec 2019}
      {{}[\href{https://linguistics.arizona.edu/gen-ed}{\textcolor{darkblue}{\faGlobe}}]}
    \resumeItemListStart
       \item Conducted weekly section meetings and office hours.
       \item Provided detailed feedback and evaluation on student's assignments.
       \item Supported students with the design of a constructed language and documenting its grammar. 
    \resumeItemListEnd
   \resumeProject
      {Teach for India, Hyderabad}
      {5th and 6th grade}
      {May 2015 - Apr 2015}
      {{}[\href{https://linguistics.arizona.edu/gen-ed}{\textcolor{darkblue}{\faGlobe}}]}
    \resumeItemListStart
       \item Taught 6th grade English and Science, and 5th grade Maths and Environmental Sciences.
       \item Participated in and conducted rigorous teacher-training programs.
       \item Raised approximately 82,000 INR to set up a digital classroom, class library and fund a sports training program. 
   \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-8mm}



\section{\textbf{Publications}\label{publications}
\hfill 
\textcolor{darkblue}{\scriptsize
                      C=Proceedings, 
                      P=Poster, 
                      W=Publication in Progress, 
                      D=Dissertation,
                      }
        }
\newrefcontext[labelprefix=C]
\vspace{0.2mm}
\nocite{*} % Ensures uncited items are included
\printbibliography[
    type=inproceedings, % Only include @article ref.bib items
    heading=none, % Do not include header. Gives us more control.
    resetnumbers=true, % Start item counter from zero
    keyword=C % Include items in ref.bib with keyword={J}
    ]
\vspace{-4mm}

\newrefcontext[labelprefix=D]
\printbibliography[
    type=thesis, % Only include @article ref.bib items
    heading=none, % Do not include header. Gives us more control.
    resetnumbers=true, % Start item counter from zero
    keyword=D % Include items in ref.bib with keyword={J}
    ]
\vspace{-4mm}

\newrefcontext[labelprefix=P]
\printbibliography[
    heading=none,
    type=misc, % Only include @article ref.bib items
    heading=none, % Do not include header. Gives us more control.
    resetnumbers=true, % Start item counter from zero
    keyword=P % Include items in ref.bib with keyword={J}
    ]
\vspace{-4mm}

\newrefcontext[labelprefix=W]
\printbibliography[
    heading=none,
    type=misc, % Only include @article ref.bib items
    heading=none, % Do not include header. Gives us more control.
    resetnumbers=true, % Start item counter from zero
    keyword=W % Include items in ref.bib with keyword={J}
    ]

\vspace{-7mm}

\section{\textbf{Skills}}\label{skills}
\vspace{-0.4mm}
    \resumeHeadingSkillStart
        \resumeSubItem{Programming and Scripting:}
        {Python, R, Praat scripting, bash scripting, grep, ssh, slurm}
        \resumeSubItem{Web Technologies:}
        {D2L, Google Docs, Panopto, Qualtrics}
        \resumeSubItem{Data and Code Management Systems:}
        {Pandas, Bee Keeper, Excel, git }
        \resumeSubItem{NLP, Data Science \& Machine Learning:}
        {Pytorch, ScikitLearn, PyKaldi, SpaCy, NLTK, Matplotlib, Pandas, Numpy, Notebooks, WhisperAI, SpeechBrain, Ollama, Jupyter}
        \resumeSubItem{NLP and Phonetics:}
        {SpaCy, NLTK, Beautiful Soup, perl, Ollama, WhisperAI, SpeechBrain, Praat, Parseltongue, Kaldi, OpenSMILE, ffmpeg}
        \resumeSubItem{Mathematical \& Statistical Tools:}
        {numpy, scipy, ggplot, lme4, dplyr, gss }
        \resumeSubItem{Other Tools \& Technologies:}
        {imagemagik, HPC, Gradio}
        \resumeSubItem{Documentation and editing:}
        { \LaTeX, MS Word, RMarkdown \& Knitr, MKdocs, Github Pages, vim, Jupyter Notebooks}
        %   \resumeSubItem{DevOps \& Version Control:}
        %     {Tool 1, Tool 2, Tool 3, Tool 4, Tool 5}
    \resumeHeadingSkillEnd
\vspace{-3mm}


\section{\textbf{Fellowships and Awards}}\label{fellowships}
\vspace{-0.4mm}
\resumeSubHeadingListStart

    \resumeProject
      {Data Science Fellowship}
      {Data Science Institute, University of Arizona}
      {Jan - Apr 2023}      {[\href{https://datascience.arizona.edu/education/data-science-fellows}{\textcolor{darkblue}{\faIcon{globe}}}]}
        \resumeItemListStart
          \item Training for data management planning, research reproducibility and accessibility, and effective
software documentation.
          \item Awarded a cash stipend of \$6000.
          \item Submitted a paper+code sample Github repository as my capstone project [\href{https://github.com/meghavarshini/foss_capstone_entrainment_detector}{\faGithub}].
        \resumeItemListEnd
    
    \resumeProject
      {Artistic Expression of Original Research}
      {Institute for Resilience, University of Arizona}
      {Oct 2024}
      {{}[\href{https://arts.arizona.edu/exhibition-brings-together-science-art-and-community-building/}{\textcolor{darkblue}{\faIcon{globe}}}]}
        \resumeItemListStart
          \item Selected to participate in a 3-day retreat, with workshops and talks on science communication, artistic techniques.
          \item Created a mixed-media installation depicting my doctoral research for three public exhibitions.
        \resumeItemListEnd
    
    \resumeProject
      {Travel award}
      {Department of Linguistics, University of Arizona}
      {July 2023}
      {}% {[\href{https://competition-link.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
        \resumeItemListStart
          \item Awarded \$1000 towards research travel to the International Congress for Phonetic Science 2023 for presenting \cite{krishnaswamy2023perception, mitracoarticulation,gp2023mismatch}.
        \resumeItemListEnd
 
    \resumeProject
      {Research Fund Award}
      {Department of Linguistics, University of Arizona}
      {February 2022}
      {}% {{}[\href{https://competition-link.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
        \resumeItemListStart
          \item Awarded \$800 towards experimental research contributing to publication \cite{krishnaswamy2023perception}.
        \resumeItemListEnd
    
    % \resumeProject
    %   {Competition Achievement}
    %   {Competition Name, Organizing Body}
    %   {Month Year}
    %   {{}[\href{https://competition-link.com}{\textcolor{darkblue}{\faIcon{globe}}}]}
    %     \resumeItemListStart
    %       \item Specific achievement or rank in the competition
    %       \item Skills or abilities demonstrated through this achievement
    %     \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-8mm}


\section{\textbf{Leadership Experience}}
\vspace{-0.4mm}
\resumeSubHeadingListStart

    \resumeProject
      {Coordinator, Arizona Linguistics Circle Conference}
      {University of Arizona}
      {May 2022 - Oct 2021}
      {{}[\href{https://easychair.org/cfp/alc16}{\textcolor{darkblue}{\faIcon{globe}}}]}
    \resumeItemListStart
        \item Build the Easychair abstracts submission portal.
        \item Recruited reviewers and coordinated the double-blind peer review.
        \item Managed all communications with authors.
        \item Created documentation for all procedures.
    \resumeItemListEnd

    \resumeProject
      {Coordinator, Arizona Linguistics Circle Conference}
      {University of Arizona}
      {May 2021 - Oct 2021}
      {{}[\href{https://sites.google.com/view/alc15}{\textcolor{darkblue}{\faIcon{globe}}}]}
    \resumeItemListStart
      \item Managed social media accounts across multiple platforms.
      \item Created PR materials for disseminating information on the conference.
      \item Created profiles for authors and their submissions.
    \resumeItemListEnd

    \resumeProject
      {Office bearer, Arizona Linguistics Circle}
      {University of Arizona}
      {Jan 2021 - Present}
      {{}[\href{https://linguistics.arizona.edu/linguistics-circle}{\textcolor{darkblue}{\faIcon{globe}}}]}
    \resumeItemListStart
      \item Represented the student body in faculty meetings.
      \item Managed equipment and amenities in the student spaces.
      \item Mentored incoming graduate students.
      \item Volunteered in presentations and university showcases.
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-6mm}

\section{\textbf{Service}}
\vspace{-0.4mm}
\resumeSubHeadingListStart
    \resumeProject
      {Instructor, Software Carpentry Workshop}
      {University of Arizona}
      {March 2025}
      {{}[\href{https://ua-carpentries-workshops.github.io/2025-03-22-Tucson/}{\textcolor{darkblue}{\faIcon{globe}}}]}
    \resumeProject
      {Instructor, Software Carpentry Workshop}
      {University of Arizona}
      {December 2023}
      {{}[\href{https://ua-carpentries-workshops.github.io/2023-12-09-Tucson/}{\textcolor{darkblue}{\faIcon{globe}}}]}

    \resumeProject
      {Reviewer, Cayote papers}
      {University of Arizona}
      {Oct 2021}
      {{}[\href{https://coyotepapers.sbs.arizona.edu/issues-coyote-papers}{\textcolor{darkblue}{\faIcon{globe}}}]}
    
    \resumeProject
      {Reviewer}
      {Peer J Computer Science}
      {Mar 2023}
      {{}[\href{https://peerj.com/computer-science/}{\textcolor{darkblue}{\faIcon{globe}}}]}
\resumeSubHeadingListEnd
\vspace{-6mm}

% \section{\textbf{Professional Memberships}}
% \vspace{-0.4mm}
% \resumeSubHeadingListStart
% \resumePOR{Professional Organization A}
%     {, Membership ID: XXXXXXXX}
%     {Month Year - Present}
% \resumePOR{Professional Organization B}
%     {, \href{https://membership-certificate-link.com}{Membership ID: XXXXXXXX}}
%     {Month Year - Present}
% \resumePOR{Professional Organization C}
%     {, \href{https://membership-certificate-link.com}{Membership ID: XXXXXXXX}}
%     {Month Year - Present}

% \resumeSubHeadingListEnd
% \vspace{-6mm}

% \section{\textbf{Certifications}}
% \vspace{-0.2mm}
% \resumeSubHeadingListStart
% \resumePOR{}{\href{https://certification-link-a.com}{
% \textbf{Certification A}
% }}{Month Year}
% \resumePOR{}{
% \textbf{Certifying Body:} {{\href{https://certification-link-b.com}{Certification B}}}}{Month Year}
% \resumePOR{}{
% \textbf{Certifying Body:} {{\href{https://certification-link-c.com}{Certification C}}}}{Month Year}
% \resumePOR{}{\href{https://certification-link-d.com}{
% \textbf{Certification D}
% }}{Month Year}

% \resumeSubHeadingListEnd
% \vspace{-6mm}

% \section{\textbf{Additional Information}}
% \vspace{-0.4mm}
% \small{
% \textbf{Languages:} English (proficient), Hindi (native), Tamil (native), German (A1).

% \textbf{Interests:} Interest 1, Interest 2, Interest 3, Interest 4
% }
% \vspace{-4mm}

% \section{\textbf{References}}
% \vspace{-0.2mm}
% \small{
% \begin{enumerate}[leftmargin=*,labelsep=2mm]
%     \item \textbf{Natasha Warner}\\
%        Professor, Department of Linguistics\\
%        The University of Arizona\\
%        Email: nwarner@arizona.edu\\
%        Phone: +1-520-626-5591\\
%        \textit{Relationship: Dissertation Advisor}
    
%     \item \textbf{Indranil Dutta}\\
%        Professor, School of Languages and Linguistics\\
%        Jadavpur University, Kolkata\\
%        Email: indranildutta.lnl@jadavpuruniversity.in\\
%        % Phone: +X-XXX-XXX-XXXX\\
%        \textit{Relationship: Principle Investigator, dst-csri project: `Influence of coarticulation on lexical access'}
    
%     \item \textbf{ Carlos Lizárraga}\\
%        Computational \& Data Scientist Educator, Data Science Institute\\
%        The University of Arizona\\
%        Email: clizarraga@arizona.edu\\
%        % Phone: +X-XXX-XXX-XXXX\\
%        \textit{Relationship: GRA Supervisor}
% \end{enumerate}
% }
% \end{itemize}
\end{document}

%%%%%%%%%%% Original Header %%%%%%%%%%%%%%%
% \begin{center}
%     \small{ \socialicon{\faEnvelope}~\href{mailto:mkrishnaswamy@arizona.edu}{mkrishnaswamy[at]arizona.edu}\\
%     \socialicon{\faGraduationCap}\href{https://linguistics.arizona.edu/person/meghavarshini-krishnaswamy/}{meghavarshini-krishnaswamy}
%     }\\
% \end{center}
% \vspace{-5.7mm}
% \begin{center}
%     \small{
%     \socialicon{\faLinkedin} \href{www.linkedin.com/in/meghavarshini-krishnaswamy}{meghavarshini-krishnaswamy}\\ 
%     \socialicon{\faGithub} \href{https://github.com/meghavarshini}{meghavarshini}\\
%     \socialicon{\faGlobe} \href{https://meghavarshini.github.io}{meghavarshini.github.io}
%     }
% \end{center}
% \vspace{-6mm}